### 2021-04-23 input/conclusion.tex
add a first complete draft for the conclusion

With the advent of the edge and IoT era, major distributed services
proposed by our community should be revised in order to mitigate as
much as possible trafic between \processes.  In this paper, we tackled
the problem of content indexing, a key service for storage systems.
\TODO{pas vraiment du content indexing}
%
More precisely, we proposed to address it as a dynamic logical partitioning of the infrastructure
that should be maintained according to replicas creations/removals and
infrastructure changes. Through an efficient scoped broadcast, each
\process composing the infrastructure knows eventually where the best
replica for a particular content is. The major difficulty is to handle
concurrent operations, each having a different scope and ensure the
correct convergence of the system. We defined multiple properties that highlight this complexity.

We proposed an implementation of this protocol called \NAME and
evaluated it on top of Peersim. The simulations confirmed the
correctness of our protocol as well as the confinement of the traffic
only where it is needed.

% 
From the technical viewpoint, this new service can easily be
integrated in storage services such as
\underline{I}nter\underline{P}lanetary \underline{F}ile
\underline{S}ystem (IPFS)~\cite{henningsen2020mapping}.  Such an integration would enabe us to
to perform additional experiments and observe the gain with 
respect to the DHT-based approach that is currently used.

@@

From the scientific viewpoint, we are currently investigating how our
proposal can be extended in orer to take into account multiple
autonomous systems. Indeed, \processes could leverage the hierarchical
properties of the Internet topology~\cite{nur2018geography} to avoid
flooding the whole systems with control information about all
partitions.
\TODO{should we highlight this at the end of the experiment}

>>>>

With the advent of the edge and IoT era, major distributed services
proposed by our community should be revised in order to mitigate as
much as possible trafic between \processes.  In this paper, we tackled
the problem of content indexing, a key service for storage systems.
%
More precisely, we proposed to address it as a dynamic logical partitioning of the infrastructure
that should be maintained according to replicas creations/removals and
infrastructure changes. Through an efficient scoped broadcast, each
\process composing the infrastructure knows eventually where the best
replica for a particular content is. The major difficulty is to handle
concurrent operations, each having a different scope, and ensure the
correct convergence of the system.
We defined, in particular,  multiple properties that highlight this complexity.
%
We proposed an implementation of this protocol called \NAME and
evaluated through simulations. Observations confirmed the
correctness of our protocol as well as the confinement of the traffic
only where it is needed.

As ongoing and future work, we are currently studying how it might be
possible to limit the scope of a partition to one autonomous system at
most. Indeed, the gain of propagating changes to \processes belonging to
another autonomous system might be negligible as the latency penalty
is mainly due to inter autonomous systems' links (\eg trans-continental
links).  Excatly, we are investigating how such a change can be
formalized and its impact on the current protocol.
%
%autonomous systems. Indeed, \processes could leverage the hierarchical
%properties of the Internet topology~\cite{nur2018geography} to avoid
%flooding the whole systems with control information about all
%partitions.
%\TODO{should we highlight this at the end of the experiment}
%
In addition to this action, it would make sense to evaluate the use of \NAME
within a concrete storage systems, such as
\underline{I}nter\underline{P}lanetary \underline{F}ile
\underline{S}ystem (IPFS)~\cite{henningsen2020mapping}.  Such an
integration would enabe us to to perform additional experiments and
observe the gain with respect to the DHT-based approach that is
currently used.

@@
